Internet of Things code deployment metrics

### 2014-11-09 opdracht_2/beamer.tex

\begin{frame}[label=sec-1-2]{Wireless sensor networks: wat zijn ze? (2)}

\includegraphics[width=\textwidth,keepaspectration=true]{intro/psumote.jpg}

@@

\begin{frame}[label=sec-1-6]{Belangrijke aspecten bij WSN design}
\begin{center}

\vfill
\begin{tabular}{l c r}
\hiddencell{1}{\includegraphics[width=0.25\textwidth,keepaspectration=true]{wsndesign/battery.png}} & \hiddencell{2}{\includegraphics[width=0.25\textwidth,keepaspectration=true]{wsndesign/density.png}} & \hiddencell{3}{\includegraphics[width=0.15\textwidth,keepaspectration=true]{wsndesign/euro.png}}  \\
\hiddencell{1}{Energieverbruik} & \hiddencell{2}{Dichtheid} & \hiddencell{3}{Goedkoop}\\
%
\hiddencell{4}{} & \hiddencell{5}{}\\
\hiddencell{4}{} & \hiddencell{5}{}\\
\hiddencell{4}{Autonoom} & \hiddencell{5}{Adaptief}
\end{tabular}
\vfill

\end{center}
\note{Consume extremely low power, operate in high volumetric densities, have low production cost and be dispensable, be autonomous and operate unattended, be adaptive to the environment.}
\end{frame}

>>>>

\begin{frame}[label=sec-1-2]{Wireless sensor networks: wat zijn ze? (2)}
\begin{figure}
\fbox{\includegraphics[height=0.78\textheight,keepaspectration=true]{intro/psumote.jpg}}
\caption{Een PSUMote}
\end{figure}

@@

\begin{frame}[label=sec-1-6]{Belangrijke aspecten bij WSN-design}
\begin{block}{energie-effici\"ent}
test
\end{block}%
\begin{block}{dichtheid}
test
\end{block}%
\begin{block}{goedkoop}
test
\end{block}%
\begin{block}{autonoom}
test
\end{block}%
\begin{block}{adaptief}
test1
\end{block}
\note{Consume extremely low power, operate in high volumetric densities, have low production cost and be dispensable, be autonomous and operate unattended, be adaptive to the environment.}
\end{frame}
